---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Strength and Diffuculties Questionnaire for R

<!-- badges: start -->
<!-- badges: end -->

The goal of sdqR is to provide access to one of the widely used questionnaires, Strength and Difficulties Questionnaire. It provides access to the questionnaire itself, includes several datasets for public use of data analysis and exploration as well as provide some means to use the questionnaire and datasets.

Currently, the package includes the following datasets:

To start using the packages, install the package using

```{r}
#install package
remotes::install_github("maria-pro/sdqR", build_vignettes = TRUE)
library(sdqR)
```

To load a dataset, use e.g.

```{r}
data<-sdq_lsac
```

## Installation - to be completed once it is on CRAN

You can install the released version of sdqR from [CRAN](https://CRAN.R-project.org) with:

``` r
#TO BE DONE
install.packages("sdqR")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("maria-pro/sdqR")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(sdqR)
## basic example code
```

